Automated Synthesis of State-Space Digital Systems

### 2016-12-21 cav2017/cav2017.tex
Added comments to Counter-Example Guided Inductive Synthesis with solution generalisation

This technique relies on parametrising the target language, which
induces a lattice of progressively more expressive languages.  We
start by attempting to synthesise a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. As well as giving us an
automatic search procedure, this parametrisation greatly increases the
efficiency of our system since languages low down the lattice are very
easy to decide safety for (i.e. the validation oracle finds an answer
fast). If a program can be synthesised in a low-complexity language,
the whole procedure finishes much faster than if synthesis had been
attempted in a high-complexity language.

\textcolor{red}{LC: Dario and Cristina, may I ask you to expand further this section by connecting it to our control-synthesis work?}
\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=6.7cm,
	minimum height=.8cm,
	label={\sc Validation oracles},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
   }   
    \\
  };

@@

\end{tikzpicture}
\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}.}
\end{figure}

>>>>

This technique relies on parametrising the target language, which
induces a lattice of progressively more expressive languages 
\textcolor{red}{Cristina: Citation?}.  We
start by attempting to synthesise a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. As well as giving us an
automatic search procedure, this parametrisation greatly increases the
efficiency of our system since languages low down the lattice are very
easy to decide safety for (i.e. the validation oracle finds an answer
fast). If a program can be synthesised in a low-complexity language,
the whole procedure finishes much faster than if synthesis had been
attempted in a high-complexity language.

\textcolor{red}{Cristina: How does this section relate to our control-synthesis work? 
This is text is too generic...}

\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=6.7cm,
	minimum height=.8cm,
	label={\sc Validation oracles},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
   }   
    \\
  };

@@

\end{tikzpicture}
\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}. 
\textcolor{red}{Cristina: What is the difference of this figure to that in our HSCC paper?}}
\end{figure}
